---
title: "Homework 3"
author: "Christine Hou"
date: "2022-10-13"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggplot2)
library(dbplyr)
library(nycflights13)
```

#### 1. Compute the average delay by destination, then join on the airports data frame so you can show the spatial distribution of delays. Here’s an easy way to draw a map of the United States:

```{r,comment=NA}
airports %>%
  semi_join(flights, c("faa" = "dest")) %>%
  ggplot(aes(lon, lat)) +
    borders("state") +
    geom_point() +
    coord_quickmap()
```

#### (Don’t worry if you don’t understand what semi_join() does — you’ll learn about it next.)

#### You might want to use the size or colour of the points to display the average delay for each airport.

```{r,comment=NA}
flights %>%
  group_by(dest) %>%
  summarize(avg_delay = mean(arr_delay, na.rm = TRUE)) %>%
  left_join(airports, by = c("dest" = "faa")) %>%
  ggplot(aes(lon, lat, size = avg_delay, color = avg_delay)) +
  borders("state") +
  geom_point() +
  coord_quickmap()
```


#### 2. Add the location of the origin and destination (i.e. the lat and lon) to flights.



#### 3. Is there a relationship between the age of a plane and its delays?

